Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-02 MultipleRoundSims/sections/04-expts.tex
ratios in results2

>>>>

We used the R2B2 library \cite{r2b2_anon}, which provides a framework for the exploration of round-by-round
and ballot-by-ballot RLAs. It has implementations of several ballot polling risk-limiting audits as well as a simulator, 
all written in Python. For each of these audits, the software can compute the stopping condition for a given sample and estimates
of the next round size to achieve a desired stopping probability. 
For a given audit and random seed, the simulator draws random samples, with replacement, using a pseudorandom number generator, given the number of votes for each candidate, and the number of invalid votes, in the underlying election (these need not be chosen to be as announced).

When the number of candidates is more than two, the audit is carried out pairwise for each candidate pair, and votes for all other candidates are considered invalid votes.

After drawing a simulated sample of ballots, the simulator evaluates the given audit's stopping condition for this sample.
If the audit stops, the simulation stops, and if the audit continues, the simulation draws another round. 
The abstract simulator class does not prescribe any one method for choosing round sizes. 
We implement several classes to support various round size choices: 
round sizes from an estimate to achieve a desired probability of stopping, 
predetermined round sizes, and pseudorandomly-generated round sizes.

### 2021-11-02 MultipleRoundSims/sections/06-results2.tex
ratios in results2

In this section we present our data on the expected number of ballots drawn as the number of rounds increases, and on the fraction of audits that stop (an estimate of cumulative stopping probability, $C_j$) for the states of Texas, Missouri and Massachusetts, with margins of $0.057$, $0.157$ and $0.342$ respectively. Interestingly, we observe that the advantage $\Minerva$ has for a first round size with stopping probability $S_1=0.9$ is retained for $S_1=0.25$.

\begin{figure}
\includegraphics[width=0.6\textwidth]{texas2.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Texas, margin $0.057$, and first round stopping probability $S_1=0.25$.}
\label{fig:texas_25}
\end{figure}

We observe that the behavior of both \Minerva audits is similar, and that the plot for SO \BRAVO is to the right (more ballots) and below (lower probability of stopping) those for \Minerva, even for a stopping probability as low as $0.25$. We observe that the plot for EoR \BRAVO shows the worst performance, which is not surprising. We observe similar behavior across margins (see Figures \ref{fig:missouri_25} and \ref{fig:mass_25}), though the improvement due to \Minerva reduces margins get larger. We see also that the behavior is similar to that seen for $S_1=0.9$ (see Figure \ref{fig:texas_90}).

\begin{figure}
\includegraphics[width=0.6\textwidth]{missouri2.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Missouri, margin $0.157$, and first round stopping probability $S_1=0.25$.}
\label{fig:missouri_25}
\end{figure}

\begin{figure}
\includegraphics[width=0.6\textwidth]{massachusetts2.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Massachusetts, margin $0.342$, and first round stopping probability $S_1=0.25$.}
\label{fig:mass_25}
\end{figure}

\begin{figure}
\includegraphics[width=0.6\textwidth]{texas1.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Texas, margin $0.057$, and first round stopping probability $S_1=0.9$.}
\label{fig:texas_90}
\end{figure}

>>>>

In this section we present our data on the expected number of ballots drawn as the number of rounds increases, and on the fraction of audits that stop (an estimate of cumulative stopping probability, $C_j$) for the states of Texas, Missouri and Massachusetts, with margins of $0.057$, $0.157$ and $0.342$ respectively. Interestingly, we observe that $\Minerva$ has an advantage for a first round size with stopping probability $S_1=0.25$, but it is not as large as that for $S_1=0.9$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\textwidth]{texas2.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Texas, margin $0.057$, and first round stopping probability $S_1=0.25$.}
\label{fig:texas_25}
\end{centering}
\end{figure}

We observe that the behavior of both \Minerva audits is similar, and that the plot for SO \BRAVO is to the right (more ballots) and below (lower probability of stopping) those for \Minerva, even for a stopping probability as low as $0.25$. We observe that the plot for EoR \BRAVO shows the worst performance, which is not surprising. We observe similar behavior across margins (see Figures \ref{fig:missouri_25} and \ref{fig:mass_25}), though the improvement due to \Minerva reduces as margins get larger. We see also that the improvement due to using \Minerva is not as large as that seen for $S_1=0.9$ (see Figure \ref{fig:texas_90}).

For $S_1=0.25$, the ratio of first round size of EoR \BRAVO to \Minerva is 1.45, 1.37, 1.23 for states Texas, Missouri and Massachusetts, and margins $0.057$, $0.157$ and $0.342$ respectively. This may be compared to $2.03$, $1.99$ and $1.8$ respectively for $S_1=0.9$.

Similarly, for $S_1=0.25$, the ratio of first round size of SO \BRAVO to \Minerva is 1.13, 1.08, 1.12 for states Texas, Missouri and Massachusetts, and margins $0.057$, $0.157$ and $0.342$ respectively. This may be compared to $1.38$, $1.38$ and $1.30$ respectively for $S_1=0.9$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\textwidth]{missouri2.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Missouri, margin $0.157$, and first round stopping probability $S_1=0.25$.}
\label{fig:missouri_25}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\textwidth]{massachusetts2.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Massachusetts, margin $0.342$, and first round stopping probability $S_1=0.25$.}
\label{fig:mass_25}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\textwidth]{texas1.png}
\caption{This plot shows the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the state of Texas, margin $0.057$, and first round stopping probability $S_1=0.9$.}
\label{fig:texas_90}
\end{centering}
\end{figure}
